An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-10-06 paper.tex
Introduction to §7

We structure the remainder of this paper as follows.
Section \ref{sec:background} introduces the IETF and the Internet Standards
development process, and reviews the data with which we work.
Section \ref{sec:trends-documents} considers trends in document production,
complexity, and correctness.
Section \ref{sec:trends-demographics} moves on to consider the people who
are involved in Internet standards development and how the demographics of
the community have shifted over time.
Section \ref{sec:org-dyn} studies the interaction between participants,
explores who has influence and impact in the IETF and how that influence
is evident in their activities, and the dynamics of communications within
the IETF.
Section \ref{sec:language} considers communications within the IETF from
the perspective of language to explore whether there are differences in
linguistic patterns and language use in more influential participants,
and to consider how the use of language reflects the consensus-driven
nature of the standards development process.
Section \ref{sec:success-factors} then considers factors that lead to
success, exploring what makes a document likely to be completed and
used, and what makes a successful participant.
Finally, we review related work in Section \ref{sec:related} and conclude
in Section \ref{sec:conclusions}.

@@

\todo{introductory remarks}

@@

Finally, the focus of our modelling in this paper has been on the impact of
document, author, and interaction-based features on protocol deployment.
However, this is only one part of the lifecycle of an RFC. It remains to
consider the impact of these, and other, features on the key stages of an
Internet-Draft's development towards becoming an RFC, such as working group
adoption.

>>>>

We structure the remainder of this paper as follows.
Section \ref{sec:background} introduces the IETF and the Internet Standards
development process, and reviews the data with which we work.
Section \ref{sec:trends-documents} considers trends in document production,
complexity, and correctness.
Section \ref{sec:trends-demographics} moves on to consider the people who
are involved in Internet standards development and how the demographics of
the community have shifted over time.
Section \ref{sec:org-dyn} studies the interaction between participants,
explores who has influence and impact in the IETF and how that influence
is evident in their activities, and the dynamics of communications within
the IETF.
Section \ref{sec:language} considers communications within the IETF from
the perspective of language to explore whether there are differences in
linguistic patterns and language use in more influential participants,
and to consider how the use of language reflects the consensus-driven
nature of the standards development process.
Section \ref{sec:success-factors} then considers factors that lead to
success, exploring what makes a document likely to be published as an
RFC and what makes a successful participant.
Finally, we review related work in Section \ref{sec:related} and conclude
in Section \ref{sec:conclusions}.

@@

Finally, we consider factors that lead to success, exploring what makes a
successful participant (\S\ref{sec:success-factors:authors}) and what makes
a document likely to be successfully published as an RFC (\S\ref{sec:success-factors:documents}).

Results show that influential authors (i.e., those with high centrality in
the email social graph) and authors affiliated with organisations that
participate strongly in IETF are more likely to have their documents
adopted and published as RFCs. However, documents that build on existing
work, have well-defined requirements, limited scope, and meet a need have
improved chances of success with authorships playing less of a role. Good,
well-connected, people are important, but so is focussed technical work.

@@

Finally, the focus of our modelling in this section has been on the impact of
document, author, and interaction-based features on protocol deployment.
However, this is only one part of the lifecycle of an RFC. It remains to
consider the impact of these, and other, features on the key stages of an
Internet-Draft's development towards becoming an RFC, such as working group
adoption.
